The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-02-09 paper.tex
remove reference to gage (#51)
pymeasure citation, use word software

We have carefully defined \yaq{} traits to maximize interoperability while not excluding hardware with unusual features.
New traits can be discussed by the community through the yaq enhancement proposal system.
It's crucial that multiple hardware interface examples be considered when defining traits.
Configuration that is unique to a single interface is best handled through protocol-specific messages.
For example, our protocol for interfacing with data acquisition cards from Gage provides a message for setting the segment count.
Unique messages are avaliable through script-based and graphical clients, but usage of such messages in scripts naturally limits portability.

@@

At the bottom, we graphically represent the integration between \yaq{} and the Bluesky project\cite{AllanDanielB2019a}.
Bluesky provides a powerful orchestration layer for conducting and recording data for a wide variety of experimental procedures.
Bluesky has no built-in hardware interface support, instead relying on packages to create hardware-interfaces that are compatible with their Hardware Protocol defintions.
\texttt{yaqc-bluesky}\footnote{\texttt{yaqc-bluesky} available on PyPI at https://pypi.org/project/yaqc-bluesky/} is a specialized client which adapts any \yaq{} protocol into Bluesky's Hardware Protocol.
Similar translation layers could be built for a variety of orchestration layers such as PyMoDAQ\cite{WeberSebastien2021a}, Instrumental\cite{Bogdanowicz2022}, or TRSpectrometer\cite{trspectrometer}.

>>>>

We have carefully defined \yaq{} traits to maximize interoperability while not excluding hardware with unusual features.
New traits can be discussed by the community through the yaq enhancement proposal system.
It's crucial that multiple hardware interface examples be considered when defining traits.
Configuration that is unique to a single interface is best handled through protocol-specific messages.
For example, our protocol for interfacing with a specific data acquisition card provides a message for setting the segment count.
Unique messages are avaliable through script-based and graphical clients, but usage of such messages in scripts naturally limits portability.

@@

At the bottom, we graphically represent the integration between \yaq{} and the Bluesky project\cite{AllanDanielB2019a}.
Bluesky provides a powerful orchestration layer for conducting and recording data for a wide variety of experimental procedures.
Bluesky has no built-in hardware interface support, instead relying on packages to create hardware-interfaces that are compatible with their Hardware Protocol defintions.
\texttt{yaqc-bluesky}\footnote{\texttt{yaqc-bluesky} available on PyPI at https://pypi.org/project/yaqc-bluesky/} is a specialized client which adapts any \yaq{} protocol into Bluesky's Hardware Protocol.
Similar translation layers could be built for a variety of orchestration software such as PyMoDAQ\cite{WeberSebastien2021a}, PyMeasure\cite{pymeasure}, or TRSpectrometer\cite{trspectrometer}.
